---
title: "Practice Presentations"
format: revealjs
---

## ABOUT DATA
These brief presentations about data will allow you to exercise your R and git skills with collaborators, use the following structure to organize your report.  


```{r, echo = TRUE}
# Displays code in slides

```

```{r, eval = TRUE, echo = FALSE}
# Run code, do not display code

```

```{r, eval = FALSE, echo = TRUE}
# Display code, DO NOT run code

```


## Summary Stats (Calculations)
What are all the variables?
Which variables may be predictors/outcomes?
How are the variables distributed?

```{r}

```

## Summary Stats (Graphics)
Use boxplots to check for outliers. Eliminate entries outside of the fence.
Use histogram to further explore variable distributions.
```{r, fig.align='center'}
# ALIGN your figures to the center of the slide

```


## Relationships
Normalize your variables, which variables are correlated, are any of your variables co-linear.


```{r, eval = T, echo = F}

```

## Visualization or Analysis

```{r}

```

## Analysis (Yuta)

```{r}
library(tidyverse)
tt=as.data.frame(Titanic)
summary(tt)
boxplot(tt)
# eliminate two outliers (Crew/Male/Adult/Not survived=670, 3rd/Male/Adult/No=387)
tt_rm <- subset(tt, Freq <= 300)

# create dummy variable
tt_rm$death <- ifelse(tt_rm$Survived == "No", 1, 0)

# calculating mortality for each variable
ByClass <- tt_rm %>%
  group_by(Class, death) %>%
  summarise(total = sum(Freq))
ByClass 
Mor_Class <- tibble(class = c("1st", "2nd", "3rd"), Mortality = c(122/(203+122), 167/(118+167), 141/(178+141)))


BySex <- tt_rm %>%
  group_by(Sex, death) %>%
  summarise(total = sum(Freq))
BySex
Mor_Sex <- tibble(sex = c("Male", "Female"), Mortality = c(307/(367+307), 126/(344+126)))

ByAge <- tt_rm %>%
  group_by(Age, death) %>%
  summarise(total = sum(Freq))
ByAge
Mor_Age <- tibble(age =c("Child", "Adult"), Mortality = c(52/(57+52), 654/(654+381)))

print(Mor_Class) # 1st = 0.375, 2nd = 0.586, 3rd = 0.442
print(Mor_Sex) # Male = 0.455, Female = 0.268
print(Mor_Age) # child = 0.477, adult = 0.632
```

This simple aggregate results showed that males had a higher mortality rate than females, and adults had a higher mortality rate than children by age.
By class, the 1st class had a lower mortality rate than the other classes.

These results may be influenced by the order of priority evacuation to the boats on the Titanic and the location of the rooms by class (1st class was the top room).

```


